Analyzing the impact of social attributes on commit integration success

### 2017-02-21 Paper/MSRChallenge2017.tex
four pager can have a shorter abstract.  Also a todo

\usepackage[usenames,dvipsnames]{color}
\newcommand{\todo}[1]
  {{\scriptsize \textbf{\color{red} {#1}}}}
\newcommand{\clg}[1]
  {{\scriptsize \textbf{\color{blue} {CLG says: #1}}}}

@@

\begin{abstract}
Software quality is an important and desirable aspect of the software 
development process. 
As the software development community continues to make it easier for everyone
to contribute, the number of commits and pull requests keep increasing.
As the number of commits and pull requests increase, it becomes more difficult
to only accept quality contributions.
Recent research has explored how the open source community manages
this question, finding that both technical and social factors are factors in 
the success of project contributions on GitHub.  
However, with continuous integration, we can
explore this question a step further.  We can better estimate the success of a
contribution by investigating if the contribution passed all the quality standards set 
by the repository owners.  We performed an initial investigation into the technical and
social factors involved in a commit that successfully passes the integration
tests. Specifically, we investigated if social factors (such as being a
core member of the development team, having a large number of followers,
or contributing a large number of commits) improve predictions of build
success.  We have found that while social factors cause a noticeable increase
in predictive power (12\%), further investigation into these factors are
required.
\end{abstract}

@@

\textbf{Related work:}
Similar studies have shown the relationship between both social and technical attributes attributes and 
different measures of success: pull request acceptance~\cite{gousios14, 
gousios15,tsay14icse,tsay14fse}, pull request evaluation latency~\cite{Yu15}.
Tsay et al.~\cite{tsay14icse} 
show that the social connection between the developer initiating a
pull request and the project integrators is a key factor in predicting 
acceptance of a pull 
request. Unlike this previous study, in our study, we look at a broader aspect of 
social aspects, and focus on predicting the success in Travis
CI jobs.Gousios et al.~\cite{gousios14} found that the change location of a commit was
an important indicator in the acceptance rate of those commits by the project.
Also, the inclusion of test cases with a commit has been shown to increase the
commit's acceptance rate~\cite{gousios15}.\todo{Zack - Mau check that the
previous sentence is correct.  I am just guessing by what you had earlier}.
tests and overall code quality~\cite{gousios15} are attributes that have a 
strong relationship with the acceptance rate of a pull request.
 Bettenburgh et 
al.~\cite{bettenburgh10} discuss the impact of social interactions with 
post-release defects, Vasilescu et al.~\cite{vasilescu14} explore how different 
project characteristics (programming language, project age, etc.) affect commit 
success when integrated into the automatic build process. Yu et al.~\cite{yu16} 
analyze the impact of CI usage in GitHub and its correlation with software 
quality. Unlike the works previously listed, we focus on independent social 
attributes and how these relate to the success of the integration of a commit 
pushed by the developer being described by these social attributes.

>>>>

\usepackage[usenames,dvipsnames]{color}
\newcommand{\todo}[1]
  {{\scriptsize \textbf{\color{red} {#1}}}}
%\newcommand{\todo}[1] {}
\newcommand{\clg}[1]
  {{\scriptsize \textbf{\color{blue} {CLG says: #1}}}}

@@

\begin{abstract}
As the software development community continues to make it easier for everyone
to contribute, the number of commits and pull requests keep increasing. However, this exciting growth
renders it more difficult to only accept quality contributions.
Recent research has found 
that both technical and social factors predict
the success of project contributions on GitHub.  
We take this question a step further, focusing on predicting continuous
integration build success based on technical and
social factors involved in a commit.
Specifically, we investigated if social factors (such as being a
core member of the development team, having a large number of followers,
or contributing a large number of commits) improve predictions of build
success.  We found that while social factors cause a noticeable increase
in predictive power (12\%), further investigation into these factors are
required.\todo{drop the post-comma clause and instead summarize the specific
  effects we investigated (contributor, followers, etc).}
\end{abstract}

@@

\textbf{Related work:}
Similar studies have shown the relationship between both social and technical attributes attributes and 
different measures of success: pull request acceptance~\cite{gousios14, 
gousios15,tsay14icse,tsay14fse}, pull request evaluation latency~\cite{Yu15}.
Tsay et al.~\cite{tsay14icse} show that the social connection between the developer initiating a
pull request and the project integrators is a key factor towards acceptance of a pull 
\todo{I think you mean something like ``in predicting acceptance'', not
  ``towards''; do they argue causality?}
request. Unlike this previous study, in our study, we look at a broader aspect of 
social aspects and how this attributes\todo{wrong word (as in, this is a noun as
  used); I'm not sure what you mean so I can't fix it.}towards the success in Travis
CI jobs.\todo{Again, why are CI jobs interesting?  If you answre it appropriatey
  above you may not need to say it again here.} \footnote{https://docs.travis-ci.com/user/customizing-the-build} 
Gousios et al.~\cite{gousios14} found that the change location of a commit was
an important indicator in the acceptance rate of those commits by the project.
Also, the inclusion of test cases with a commit has been shown to increase the
commit's acceptance rate~\cite{gousios15}.\todo{Zack - Mau check that the
previous sentence is correct.  I am just guessing by what you had earlier}.
tests and overall code quality~\cite{gousios15} are attributes that have a 
strong relationship with the acceptance rate of a pull request.
 Bettenburgh et 
al.~\cite{bettenburgh10} discuss the impact of social interactions with 
post-release defects, Vasilescu et al.~\cite{vasilescu14} explore how different 
project characteristics (programming language, project age, etc.) affect commit 
success when integrated into the automatic build process. Yu et al.~\cite{yu16} 
analyze the impact of CI usage in GitHub and its correlation with software 
quality. Unlike the works previously listed, we focus on independent social 
attributes and how these relate to the success of the integration of a commit 
pushed by the developer being described by these social attributes.
